Karbowski model in 2-D

### 2020-05-26 paper/supplementary/supp.tex
Removes irrelevant eqn
Adds note about no need for sigmoid

This modifies the axon branching with a similar term to Eq.~\ref{eq:chibard},
depending on the gradient of $\hat{a}_i = \sum_{j\ne i}{a_j}$. However, here,
the term is included in the \emph{flux of axonal branching}
(i.e.~\emph{inside} the brackets) and so its divergence is taken and this
contributes a scalar quantity to the change of $a_i$. Two other points to note
about Eq.~\ref{eq:da_comp2_elife}: I included a scalar parameter $F$ to modify
the relative contribution of this term; and $\bar{a}_i$ is the result of
passing $a_i$ through a sigmoidal transfer function (see Eq.~\ref{eq:abar})
which I found necessary to prevent the term from becoming numerically
unstable.

@@

\begin{equation}\label{eq:chibard_mag}
\chi_i = \frac{a_i}{N-1} \| \nabla\hat{a}_i\|.
\end{equation}

>>>>

This modifies the axon branching with a similar term to Eq.~\ref{eq:chibard},
depending on the gradient of $\hat{a}_i = \sum_{j\ne i}{a_j}$. However, here,
the term is included in the \emph{flux of axonal branching}
(i.e.~\emph{inside} the brackets) and so its divergence is taken and this
contributes a scalar quantity to the change of $a_i$. Two other points to note
about Eq.~\ref{eq:da_comp2_elife}: I included a scalar parameter $F$ to modify
the relative contribution of this term; and $\bar{a}_i$ is the result of
passing $a_i$ through a sigmoidal transfer function (see Eq.~\ref{eq:abar})
which I found necessary to prevent the term from becoming numerically
unstable.*

@@

*: Ah, no sigmoid transfer function required. With $\bar{a}_i = a_i$ the
 system runs successfully, although for a limited parameter range. The system
 can be made slightly more stable by making
%
\begin{equation}
\begin{split}
\bar{a}_i & = a_i, a<a_{max} \\
          & = a_{max}, a\geq a_{max}
\end{split}
\end{equation}
